---
title: "main_network"
author: "Zeyu Hu"
date: "2024-11-19"
output: html_document
---

## read data
```{r echo=FALSE}
# 加载必要的包
library(igraph)
library(dplyr)

# 读取数据表
nodes <- read.csv("/Users/huzeyu/Desktop/UConnHealth/Seoul network/data/Seoul_node_info.csv")
network <- read.csv("/Users/huzeyu/Desktop/UConnHealth/Seoul network/data/network.csv")

# 将合并后的 network 数据表创建图并命名为 g
g <- graph_from_data_frame(d = network, directed = TRUE)

# 设置边的权重
E(g)$weight <- network$strength

# 为每个节点添加 gu 和 dong 属性
V(g)$gu <- nodes$gu[match(V(g)$name, nodes$node)]
V(g)$dong <- nodes$dong[match(V(g)$name, nodes$node)]
V(g)$population <- nodes$population[match(V(g)$name, nodes$node)]
V(g)$business <- nodes$business[match(V(g)$name, nodes$node)]
# 创建 adjacency matrix
adjmatrix <- as_adjacency_matrix(g, sparse = FALSE, attr = "weight")
adjnull <- `rownames<-`(`colnames<-`(adjmatrix, NULL), NULL)

# 获取每条边的起点和终点的 gu 属性
edge_gu <- apply(ends(g, E(g)), 1, function(edge) {
  c(V(g)[edge[1]]$gu, V(g)[edge[2]]$gu)
})

# 转置矩阵以便使用列索引
edge_gu <- t(edge_gu)

# 创建 withingu 子图：保留同一地区 (gu) 的边，删除跨地区的边
withingu <- delete_edges(g, E(g)[edge_gu[, 1] != edge_gu[, 2]])
adj_withingu <- as_adjacency_matrix(withingu, sparse = FALSE, attr = "weight")
adjnull_withingu <- `rownames<-`(`colnames<-`(adj_withingu, NULL), NULL)

# 创建 acrossgu 子图：保留跨地区 (gu) 的边，删除同一地区的边
acrossgu <- delete_edges(g, E(g)[edge_gu[, 1] == edge_gu[, 2]])
adj_acrossgu <- as_adjacency_matrix(acrossgu, sparse = FALSE, attr = "weight")
adjnull_acrossgu <- `rownames<-`(`colnames<-`(adj_acrossgu, NULL), NULL)
```

## density

#Density is the ratio of lines or arcs present to the maximum possible that could arise. Another way to view the density of a graph or digraph is the average of the values assigned to the lines/ arcs. In unweighted networks, each line of arc is given value of 1 and absent lines are given a value of 0.

#To generalize the notion of density to a valued graph, one can average the values attached to the lines/arcs across all lines/arcs. So density of a valued graph is the sum of values of the lines divided by g(g-1). (Section 4.5.2 in Social Network Analysis Methods and Applications by Wasserman and Faust)

```{r echo=FALSE}
# 全图 weighted density
density_full <- sum(E(g)$weight) / (424^2)

# withingu weighted density
density_withingu <- sum(E(withingu)$weight) / 7470

# acrossgu weighted density
density_acrossgu <- sum(E(acrossgu)$weight) / 172306

# 输出结果
cat("Full graph weighted density:", density_full, "\n")
sprintf("The within-group density is %.2f", density_withingu)
cat("Across-gu weighted density:", density_acrossgu, "\n")
```
Full graph weighted density: 85805.07 
Within-gu weighted density: 1070829 
Across-gu weighted density: 43101.24 

## assort
```{r echo=FALSE}
library(wdnet)
assort <- assortcoef(adj = adjnull, directed = TRUE)
assort_within <- assortcoef(adj = adjnull_withingu, directed = TRUE)
assort_across <- assortcoef(adj = adjnull_acrossgu, directed = TRUE)
assortativity_popu <- assortcoef(adj = adjnull, f1 = nodes$population, f2 = NULL)$"f1-f1"
assortativity_popu_within <- assortcoef(adj = adjnull_withingu, f1 = nodes$population, f2 = NULL)$"f1-f1"
assortativity_popu_across <- assortcoef(adj = adjnull_acrossgu, f1 = nodes$population, f2 = NULL)$"f1-f1"


assortativity_business <- assortcoef(adj = adjnull, f1 = nodes$business, f2 = NULL)$"f1-f1"
assortativity_business_within <- assortcoef(adj = adjnull_withingu, f1 = nodes$business, f2 = NULL)$"f1-f1"
assortativity_business_across <- assortcoef(adj = adjnull_acrossgu, f1 = nodes$business, f2 = NULL)$"f1-f1"


# 输出结果，保留三位小数
cat("Full graph assortativity:", sprintf("%.3f", assort$outin), "\n")
cat("Within-gu assortativity:", sprintf("%.3f", assort_within$outin), "\n")
cat("Across-gu assortativity:", sprintf("%.3f", assort_across$outin), "\n")
cat("Population assortativity (Full):", sprintf("%.3f", assortativity_popu), "\n")
cat("Population assortativity (Within-gu):", sprintf("%.3f", assortativity_popu_within), "\n")
cat("Population assortativity (Across-gu):", sprintf("%.3f", assortativity_popu_across), "\n")

cat("Business assortativity (Full):", sprintf("%.3f", assortativity_business), "\n")
cat("Business assortativity (Within-gu):", sprintf("%.3f", assortativity_business_within), "\n")
cat("Business assortativity (Across-gu):", sprintf("%.3f", assortativity_business_across), "\n")
```
Full graph assortativity: 0.279 
Within-gu assortativity: 0.580 
Across-gu assortativity: -0.009 
Population assortativity (Full): 0.292 
Population assortativity (Within-gu): 0.527 
Population assortativity (Across-gu): 0.049 
Business assortativity (Full): 0.293 
Business assortativity (Within-gu): 0.618 
Business assortativity (Across-gu): 0.000  

## assort CI
```{r echo=FALSE}
library(wdnet)
library(progress)

# 定义函数计算assortativity值
define_assort <- function(adj_matrix, nodes, metric) {
  if (metric == "population") {
    return(assortcoef(adj = adj_matrix, f1 = nodes$population, f2 = NULL)$"f1-f1")
  } else if (metric == "business") {
    return(assortcoef(adj = adj_matrix, f1 = nodes$business, f2 = NULL)$"f1-f1")
  } else {
    return(assortcoef(adj = adj_matrix, directed = TRUE)$outin)
  }
}

# Jackknife计算置信区间
define_jackknife <- function(adj_matrix, nodes, metric) {
  n <- nrow(adj_matrix)
  values <- numeric(n) # 存储每次删除一个节点的值
  pb <- progress_bar$new(total = n, format = "Progress [:bar] :percent Elapsed: :elapsed")
  
  for (i in 1:n) {
    adj_jack <- adj_matrix[-i, -i] # 删除第i行和第i列
    values[i] <- define_assort(adj_jack, nodes[-i, ], metric) # 计算assortativity值
    pb$tick()
  }
  
  mean_value <- mean(values)
  sd_value <- sd(values)
  ci_lower <- mean_value - 1.96 * sd_value
  ci_upper <- mean_value + 1.96 * sd_value
  
  return(list(mean = mean_value, ci_lower = ci_lower, ci_upper = ci_upper))
}

# 初始化结果存储
results <- list()

# Full graph assortativity
results$assort_full <- define_jackknife(adjnull, nodes, "general")
results$assort_within <- define_jackknife(adjnull_withingu, nodes, "general")
results$assort_across <- define_jackknife(adjnull_acrossgu, nodes, "general")

# Population assortativity
results$popu_full <- define_jackknife(adjnull, nodes, "population")
results$popu_within <- define_jackknife(adjnull_withingu, nodes, "population")
results$popu_across <- define_jackknife(adjnull_acrossgu, nodes, "population")

# Business assortativity
results$business_full <- define_jackknife(adjnull, nodes, "business")
results$business_within <- define_jackknife(adjnull_withingu, nodes, "business")
results$business_across <- define_jackknife(adjnull_acrossgu, nodes, "business")

# 输出结果函数
output_results <- function(name, result) {
  cat(name, ": Mean =", sprintf("%.3f", result$mean),
      ", CI = [", sprintf("%.3f", result$ci_lower), ",", sprintf("%.3f", result$ci_upper), "]\n")
}

# 输出所有结果
output_results("Full graph assortativity", results$assort_full)
output_results("Within-gu assortativity", results$assort_within)
output_results("Across-gu assortativity", results$assort_across)
output_results("Population assortativity (Full)", results$popu_full)
output_results("Population assortativity (Within-gu)", results$popu_within)
output_results("Population assortativity (Across-gu)", results$popu_across)
output_results("Business assortativity (Full)", results$business_full)
output_results("Business assortativity (Within-gu)", results$business_within)
output_results("Business assortativity (Across-gu)", results$business_across)
```

## community detection
```{r echo=FALSE}
# Infomap 社区检测
infomap_community <- cluster_infomap(g)

# 提取社区成员分配结果
community_membership <- membership(infomap_community)

# 转换为数据框并统计每个社区的节点数量
membership_df <- data.frame(
  node = names(community_membership),
  community = community_membership
)

# 按社区统计节点数量，并按节点数量降序排列
community_sizes <- membership_df %>%
  group_by(community) %>%
  summarise(size = n()) %>%
  arrange(desc(size)) %>%
  mutate(new_community = row_number())  # 重新排列社区编号

# 将新的社区编号映射到原始数据
membership_df <- membership_df %>%
  left_join(community_sizes, by = "community") %>%
  mutate(community = new_community) %>%
  select(-new_community)

# 将重新排列的社区结果更新回原来的格式
community_membership <- setNames(membership_df$community, membership_df$node)
```

## centrality
```{r echo=FALSE}
strength_data <- data.frame(
  node = V(g)$name,  
  in_strength = strength(g, mode = "in"),
  out_strength = strength(g, mode = "out")
)

library(wdnet)
myclose_out <- centrality(
  adj = adjmatrix,
  measure = "closeness", 
  closeness.control = list(method = "harmonic", distance = FALSE, mode = "out")
)
myclose_out <- as.data.frame(myclose_out)

myclose_in <- centrality(
  adj = adjmatrix,
  measure = "closeness", 
  closeness.control = list(method = "harmonic", distance = FALSE, mode = "in")
)
myclose_in <- as.data.frame(myclose_in)

mywpr_null <- centrality(
  adj = adjmatrix,
  measure = "wpr", 
  wpr.control = list(gamma = 0.85, theta = 1)
)
mywpr_null <- as.data.frame(mywpr_null)

hub_scores <- hub_score(g)$vector
authority_scores <- authority_score(g)$vector
```

## strength distribution(powerlaw test)
```{r echo=FALSE}
# 加载必要的包
library(poweRlaw)

# 针对 in_strength 进行 power-law 测试
in_strength_data <- strength_data$in_strength
in_strength_data <- in_strength_data/1000000
in_strength_data <- floor(in_strength_data)
# 创建 power-law 分布对象
m_pl_in <- displ$new(in_strength_data)

# 估计参数
est_in <- estimate_xmin(m_pl_in)
m_pl_in$setXmin(est_in)

# 绘图
plot(m_pl_in, main = "In-strength Power Law Fit")
lines(m_pl_in, col = 2)

# 设置随机种子
set.seed(123)

# Bootstrap 检验
bs_in <- bootstrap_p(m_pl_in, no_of_sims = 100, threads = 1)

# 输出 in-strength 结果
cat("In-strength P-value:", bs_in$p, "\n")
cat("In-strength xmin:", m_pl_in$xmin, "\n")
cat("In-strength pars (alpha):", m_pl_in$pars, "\n")
cat("In-strength xmin standard error:", sd(bs_in$bootstraps$xmin), "\n")
cat("In-strength pars standard error:", sd(bs_in$bootstraps$pars), "\n\n")

# 针对 out_strength 进行 power-law 测试
out_strength_data <- strength_data$out_strength
out_strength_data <- out_strength_data/1000000
out_strength_data <- floor(out_strength_data)

# 创建 power-law 分布对象
m_pl_out <- displ$new(out_strength_data)

# 估计参数
est_out <- estimate_xmin(m_pl_out)
m_pl_out$setXmin(est_out)

# 绘图
plot(m_pl_out, main = "Out-strength Power Law Fit")
lines(m_pl_out, col = 2)

# Bootstrap 检验
bs_out <- bootstrap_p(m_pl_out, no_of_sims = 100, threads = 1)

# 输出 out-strength 结果
cat("Out-strength P-value:", bs_out$p, "\n")
cat("Out-strength xmin:", m_pl_out$xmin, "\n")
cat("Out-strength pars (alpha):", m_pl_out$pars, "\n")
cat("Out-strength xmin standard error:", sd(bs_out$bootstraps$xmin), "\n")
cat("Out-strength pars standard error:", sd(bs_out$bootstraps$pars), "\n")
```

In-strength P-value: 0.15 
In-strength xmin: 39 
In-strength pars (alpha): 3.510138 
In-strength xmin standard error: 5.534867 
In-strength pars standard error: 0.2568563 

Out-strength P-value: 0.39 
Out-strength xmin: 40 
Out-strength pars (alpha): 3.592371 
Out-strength xmin standard error: 5.885987 
Out-strength pars standard error: 0.3234717 

## strength dist(plot)
```{r echo=FALSE}
library(ggplot2)
library(ggpubr)

# In-Strength 分布
# 计算 In-Strength 的 CDF
in_cdf_data <- data.frame(
  strength = sort(in_strength_data),
  cdf = ecdf(in_strength_data)(sort(in_strength_data))
)

# 计算右尾累计分布 (1 - CDF)
in_cdf_data$tail_cdf <- 1 - in_cdf_data$cdf

# 绘制 In-Strength 右尾累计分布图
in_strength_plot <- ggplot(in_cdf_data, aes(x = strength, y = tail_cdf)) +
  geom_point(aes(color = ifelse(strength >= 39, "Above Threshold", "Below Threshold"))) +
  scale_y_log10() +
  scale_x_log10(breaks = c(1, 10, 39, 100), expand = c(0, 0)) +
  labs(
    x = "Node In-Strength (log scale)",
    y = "Survival (log scale)"
  ) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 16),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  ) +
  scale_color_manual(values = c("Below Threshold" = "black", "Above Threshold" = "blue")) +
  {
    xmin <- 39
    alpha <- 3.510138
    fitted_x <- seq(xmin, max(in_cdf_data$strength), length.out = 100)
    fitted_y <- (fitted_x / xmin)^(-alpha + 1)
    y_baseline <- in_cdf_data$tail_cdf[in_cdf_data$strength == xmin]
    fitted_y <- fitted_y * y_baseline
    geom_line(data = data.frame(strength = fitted_x, tail_cdf = fitted_y),
              aes(x = strength, y = tail_cdf), color = "red", linetype = "dashed", linewidth = 0.8)
  } +
  geom_vline(xintercept = 39, linetype = "dashed", color = "black")

# Out-Strength 分布
# 计算 Out-Strength 的 CDF
out_cdf_data <- data.frame(
  strength = sort(out_strength_data),
  cdf = ecdf(out_strength_data)(sort(out_strength_data))
)

# 计算右尾累计分布 (1 - CDF)
out_cdf_data$tail_cdf <- 1 - out_cdf_data$cdf

# 绘制 Out-Strength 右尾累计分布图
out_strength_plot <- ggplot(out_cdf_data, aes(x = strength, y = tail_cdf)) +
  geom_point(aes(color = ifelse(strength >= 40, "Above Threshold", "Below Threshold"))) +
  scale_y_log10() +
  scale_x_log10(breaks = c(1, 10, 40, 100), expand = c(0, 0)) +
  labs(
    x = "Node Out-Strength (log scale)",
    y = "Survival (log scale)"
  ) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 16),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  ) +
  scale_color_manual(values = c("Below Threshold" = "black", "Above Threshold" = "blue")) +
  {
    xmin <- 40
    alpha <- 3.592371
    fitted_x <- seq(xmin, max(out_cdf_data$strength), length.out = 100)
    fitted_y <- (fitted_x / xmin)^(-alpha + 1)
    y_baseline <- out_cdf_data$tail_cdf[out_cdf_data$strength == xmin]
    fitted_y <- fitted_y * y_baseline
    geom_line(data = data.frame(strength = fitted_x, tail_cdf = fitted_y),
              aes(x = strength, y = tail_cdf), color = "red", linetype = "dashed", linewidth = 0.8)
  } +
  geom_vline(xintercept = 40, linetype = "dashed", color = "black")

# 将 In-Strength 和 Out-Strength 图表并排排列
strength_dist_plot <- ggarrange(
  in_strength_plot,  # In-Strength 图
  out_strength_plot, # Out-Strength 图
  ncol = 2, nrow = 1  # 设置并排显示，1 行 2 列
)

# 保存联合图为 PNG 文件
#ggsave(filename = "/Users/huzeyu/Desktop/UConnHealth/Seoul network/result/strength_dist.png",  plot = strength_dist_plot,width = 12,height = 6,dpi = 300,  bg = "white")
```


## map
```{r echo=FALSE}
library(sf)
library(ggplot2)
library(geojsonio)

# 读取 TopoJSON 文件
seoul_map <- geojson_read("/Users/huzeyu/Desktop/UConnHealth/Seoul network/data/skorea-submunicipalities-2018-topo.json", what = "sp")

# 假设 seoul_map 已是 sf 格式，筛选首尔区域
seoul_map_11 <- st_as_sf(seoul_map[substr(seoul_map@data$code, 1, 2) == "11", ])

# 提取 gu 信息（前 4 位代码）
seoul_map_11 <- seoul_map_11 %>%
  mutate(gu = substr(code, 1, 4))  # 添加 gu 列

# 按 gu 合并，计算每个 gu 的边界
gu_boundaries <- seoul_map_11 %>%
  group_by(gu) %>%
  summarise(geometry = st_union(geometry))  # 合并 geometry

# 提取社区检测结果并加入到原地图数据
membership_df <- data.frame(
  code = names(community_membership),
  community = as.factor(community_membership)
)

seoul_map_11 <- seoul_map_11 %>%
  left_join(membership_df, by = c("code" = "code"))

gu_boundaries_lines <- st_cast(gu_boundaries, "MULTILINESTRING")

# 手动指定每个社区的颜色
community_colors <- c(
  "1" = "#d35f00",  # 社区 1 的颜色
  "2" = "#fd7c1a",  # 社区 2 的颜色
  "3" = "#fcff07",  # 社区 3 的颜色
  "4" = "#fe9376",  # 社区 4 的颜色
  "5" = "#f3dee0",  # 社区 5 的颜色
  "6" = "#ffbd15",  # 社区 6 的颜色
  "7" = "#a0c9e5",  # 社区 7 的颜色
  "8" = "#1d9bf7",  # 社区 8 的颜色
  "9" = "#303cf9",  # 社区 9 的颜色
  "10" = "#b4403e", # 社区 10 的颜色
  "11" = "#603c87"  # 社区 11 的颜色
)

# 绘制社区地图
community_map <- ggplot() +
  geom_sf(data = seoul_map_11, aes(fill = community), color = "grey", size = 0.2) +  # dong 分界线为灰色
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu 边界线为黑色且加粗
  scale_fill_manual(values = community_colors) +  # 手动指定颜色
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) +
  guides(
    fill = guide_legend(nrow = 2, byrow = TRUE)
  )
#ggsave("/Users/huzeyu/Desktop/UConnHealth/Seoul network/result/community_map.png", community_map, width = 8, height = 6, dpi = 300, bg = "white")
```
## centrality table
```{r echo=FALSE}
centrality <- data.frame(
  name = myclose_out$name,
  closeness_out = myclose_out$closeness,
  closeness_in = myclose_in$closeness,
  wpr = mywpr_null$wpr
)

centrality$hub <- hub_scores
centrality$authority <- authority_scores
centrality <- merge(
  centrality,     # 主表
  nodes,              # 需要合并的表
  by.x = "name",      # centrality 的匹配列
  by.y = "node",      # nodes 的匹配列
  all.x = TRUE        # 保留 centrality 中的所有行
)
centrality <- centrality %>% 
  left_join(strength_data, by = c("name" = "node"))
centrality <- centrality %>%
  dplyr::mutate(community = community_membership[name])
```

## Within/Across weighted Density
```{r echo=FALSE}
library(igraph)
library(dplyr)

# 获取边列表并包括权重
edges_df <- igraph::as_data_frame(g, what = "edges")

# 将社区分配映射到边列表
edges_df <- edges_df %>%
  mutate(
    source_community = as.factor(community_membership[as.character(from)]),
    target_community = as.factor(community_membership[as.character(to)])
  )

# 计算每个社区的节点数
community_sizes <- membership_df %>%
  group_by(community) %>%
  summarise(size = n(), .groups = "drop")

# 计算加权密度矩阵
density_matrix <- edges_df %>%
  group_by(source_community, target_community) %>%
  summarise(
    total_weight = sum(weight), # 社区对之间的总权重
    .groups = "drop"
  ) %>%
  left_join(community_sizes, by = c("source_community" = "community")) %>%
  rename(size_source = size) %>%
  left_join(community_sizes, by = c("target_community" = "community")) %>%
  rename(size_target = size) %>%
  mutate(
    possible_edges = ifelse(
      source_community == target_community, # 判断是否是社区内部
      size_source^2,                        # 社区内部：n_i^2
      2 * size_source * size_target         # 跨社区：2 * n_i * n_j
    ),
    weighted_density = total_weight / possible_edges # 加权密度
  ) %>%
  select(source_community, target_community, weighted_density)

# 转换为矩阵格式
density_matrix_wide <- density_matrix %>%
  tidyr::pivot_wider(
    names_from = target_community,
    values_from = weighted_density,
    names_prefix = "Community_"
  ) %>%
  arrange(source_community)

# 将矩阵转换为最终格式
density_matrix_final <- as.matrix(density_matrix_wide %>% select(-source_community))
rownames(density_matrix_final) <- paste0("Community_", density_matrix_wide$source_community)

# 输出结果
print("Weighted Density Matrix:")
print(density_matrix_final)

# 每个元素除以 1000，并保留 2 位小数
density_matrix_final_divided <- round(density_matrix_final / 1000, 2)

# 输出结果
print(density_matrix_final_divided)
# 将矩阵转换为数据框（CSV 友好的格式）
density_matrix_final_df <- as.data.frame(density_matrix_final_divided)

# 加载必要的包
library(ggplot2)
library(reshape2)

# 假设你的数据已经读取为 density_matrix_final_divided
# 将矩阵转换为长格式
density_long <- reshape2::melt(as.matrix(density_matrix_final_divided))

# 确保列名正确
colnames(density_long) <- c("source", "target", "Density")

# 替换标签为更简洁的格式
density_long$source <- gsub("Community_", "C-", density_long$source)
density_long$target <- gsub("Community_", "C-", density_long$target)

# 保证 x 和 y 轴顺序按照输入数据排列
unique_labels <- unique(density_long$source) # 获取原始顺序
density_long$source <- factor(density_long$source, levels = rev(unique_labels)) # 反转 y 轴顺序
density_long$target <- factor(density_long$target, levels = unique_labels) # 保持 x 轴顺序

# 对数据进行调整 (这里用对数平滑处理)
density_long$Adjusted_Density <- log(density_long$Density)

# 绘制热图
W_A_density_heatmap <- ggplot(density_long, aes(x = target, y = source, fill = Adjusted_Density)) + 
  geom_tile(color = "white") + # 添加白色边框
  geom_text(aes(label = sprintf("%.2f", Adjusted_Density)), size = 3, color = "black") + # 在格子中添加具体数值，强制保留两位小数
  scale_fill_gradientn(
    colors = c("white", "red"),
    name = "Log of Weighted Density (in thousands)" # 更新图例名称
  ) + 
  scale_x_discrete(position = "top") + # 将 x 轴放到顶部
  theme_minimal() + # 最小主题
  theme(
    axis.text.x = element_text(size = 10), # x轴标签大小
    axis.text.y = element_text(size = 10), # y轴标签大小
    legend.position = "bottom", # 图例放在下面
    legend.direction = "horizontal" # 图例横向排列
  ) + 
  labs(x = "Target", y = "Source") # 保留 x 和 y 轴标签
ggsave("../result/W_A_density_heatmap.png", 
       W_A_density_heatmap, width = 8, height = 6, dpi = 600, bg = "white")     
```

## potential maps
```{r echo=FALSE}
map_color <- nodes %>% 
  mutate(node = as.character(node))
# 将 population 添加到地图数据中
seoul_map_11 <- seoul_map_11 %>% 
  left_join(map_color, by = c("code" = "node"))  # 使用 nodes 的 node 与地图的 code 匹配

# 将 centrality 数据与地图数据合并
seoul_map_11 <- seoul_map_11 %>%
  left_join(centrality, by = c("code" = "name"))

# 绘制基于 wpr 的热图
heatmap <- ggplot(data = seoul_map_11) +
  geom_sf(aes(fill = wpr), color = "grey", size = 0.2) +  # dong 分界线为灰色
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu 边界线为黑色且加粗
  scale_fill_gradient(low = "white", high = "red") +  # 白色到红色，无图例
  theme_minimal() +
  theme(
    legend.position = "none",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  )
heatmap
# 创建地图，按 population 绘制颜色深浅
population_map <- ggplot() + 
  geom_sf(data = seoul_map_11, aes(fill = population), color = "grey", size = 0.2) +  # dong 分界线为灰色
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu 边界线为黑色且加粗
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Population") +  # 按人口深浅着色
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) + 
  guides(
    fill = guide_colorbar(barwidth = 10, barheight = 0.5)  # 调整图例的比例
  )
business_map <- ggplot() + 
  geom_sf(data = seoul_map_11, aes(fill = business), color = "grey", size = 0.2) +  # dong 分界线为灰色
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu 边界线为黑色且加粗
  scale_fill_gradient(low = "lightgreen", high = "darkgreen", name = "Business") +  # 按人口深浅着色
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) + 
  guides(
    fill = guide_colorbar(barwidth = 10, barheight = 0.5)  # 调整图例的比例
  )
incidence_map <- ggplot() + 
  geom_sf(data = seoul_map_11, aes(fill = incidence), color = "grey", size = 0.2) +  # dong 分界线为灰色
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu 边界线为黑色且加粗
  scale_fill_gradient(low = "coral", high = "darkred", name = "Incidence") +  # 按人口深浅着色
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) + 
  guides(
    fill = guide_colorbar(barwidth = 10, barheight = 0.5)  # 调整图例的比例
  )
poverty_map <- ggplot() + 
  geom_sf(data = seoul_map_11, aes(fill = poverty), color = "grey", size = 0.2) +  # dong 分界线为灰色
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu 边界线为黑色且加粗
  scale_fill_gradient(low = "coral", high = "darkred", name = "Poverty") +  # 按人口深浅着色
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) + 
  guides(
    fill = guide_colorbar(barwidth = 10, barheight = 0.5)  # 调整图例的比例
  )
poverty_map
population_map
business_map
incidence_map
heatmap
ggsave("/Users/huzeyu/Desktop/UConnHealth/Seoul network/result/population_map.png", 
       population_map, width = 8, height = 6, dpi = 300, bg = "white")
ggsave("/Users/huzeyu/Desktop/UConnHealth/Seoul network/result/business_map.png", 
       business_map, width = 8, height = 6, dpi = 300, bg = "white")
ggsave("/Users/huzeyu/Desktop/UConnHealth/Seoul network/result/incidence_map.png", 
       incidence_map, width = 8, height = 6, dpi = 300, bg = "white")
ggsave("/Users/huzeyu/Desktop/UConnHealth/Seoul network/result/wpr_heatmap.png", 
       heatmap, width = 8, height = 6, dpi = 300, bg = "white")
ggsave("/Users/huzeyu/Desktop/UConnHealth/Seoul network/result/poverty_map.png", 
       poverty_map, width = 8, height = 6, dpi = 300, bg = "white")         
```

## number of nodes for each community
```{r echo=FALSE}
library(dplyr)

# 确保两列类型一致
membership_df <- membership_df %>%
  mutate(code = as.integer(code))  # 将 code 转换为整数

nodes <- nodes %>%
  mutate(node = as.integer(node))  # 确保 node 也是整数

library(dplyr)

community_stats <- membership_df %>%
  left_join(nodes, by = c("code" = "node")) %>%
  group_by(community) %>%
  summarise(
    size = n(),
    total_population = sum(population, na.rm = TRUE),
    total_business = sum(business, na.rm = TRUE),
    total_poverty = sum(poverty, na.rm = TRUE),
    avg_population = total_population / size,
    avg_business = total_business / size,
    avg_poverty = total_poverty / size
  ) %>%
  mutate(
    size = as.numeric(size), # 转为数值型
    total_population = round(total_population, 2),
    total_business = round(total_business, 2),
    total_poverty = round(total_poverty, 2),
    avg_population = round(avg_population, 2),
    avg_business = round(avg_business, 2),
    avg_poverty = round(avg_poverty, 2)
  ) %>%
  arrange(desc(size))

# 查看结果
print(community_stats)
```

## Spearman correlation
```{r echo=FALSE}
size_rank <- rank(community_stats$size)
population_rank <- rank(community_stats$total_population)
business_rank <- rank(community_stats$total_business)
poverty_rank <- rank(community_stats$avg_poverty)

# 计算相关性系数
correlation_population <- cor(size_rank, population_rank, method = "spearman")
correlation_business <- cor(size_rank, business_rank, method = "spearman")
correlation_poverty <- cor(size_rank, poverty_rank, method = "spearman")

# 输出结果
cat("Spearman correlation coefficients:\n")
cat("Size vs Total Population:", correlation_population, "\n")
cat("Size vs Total Business:", correlation_business, "\n")
cat("Size vs Avg Poverty:", correlation_poverty, "\n")
```

## construct subnetwork for each community
```{r echo=FALSE}
# Initialize a list to store subgraphs
subnetworks <- list()

# Iterate over each community and extract subgraphs
for (i in 1:11) {
  # Select nodes belonging to the current community
  community_nodes <- names(community_membership[community_membership == i])
  
  # Extract the subgraph from the original graph and store it in the list
  subnetworks[[paste0("subnetwork", i)]] <- induced_subgraph(g, vids = community_nodes)
}
```

## community-level assort/density
```{r echo=FALSE}
# Load network data and create graphs
network2020 <- read.csv("/Users/huzeyu/Desktop/UConnHealth/Seoul network/data/network_2020.csv")
g_2020 <- graph_from_data_frame(d = network2020, directed = TRUE)
E(g_2020)$weight <- network2020$strength

network2021 <- read.csv("/Users/huzeyu/Desktop/UConnHealth/Seoul network/data/network_2021.csv")
g_2021 <- graph_from_data_frame(d = network2021, directed = TRUE)
E(g_2021)$weight <- network2021$strength

network2022 <- read.csv("/Users/huzeyu/Desktop/UConnHealth/Seoul network/data/network_2022.csv")
g_2022 <- graph_from_data_frame(d = network2022, directed = TRUE)
E(g_2022)$weight <- network2022$strength

# Initialize a data frame to store results
community_level_result <- data.frame(
  community = paste0("C-", 1:11),  # Community names
  strength_assort = numeric(11),
  popu_assort = numeric(11),
  business_assort = numeric(11),
  density_2020 = integer(11),
  density_2021 = integer(11),
  density_2022 = integer(11),
  total = integer(11)
)

# Define a function to calculate weighted density for a given graph
calculate_weighted_density <- function(graph, community_membership) {
  densities <- numeric(11)
  for (i in 1:11) {
    # Extract nodes in the current community
    community_nodes <- names(community_membership[community_membership == i])
    subgraph <- induced_subgraph(graph, vids = community_nodes)
    
    # Calculate weighted density
    total_weight <- sum(E(subgraph)$weight)  # Sum of all edge weights
    num_nodes <- length(V(subgraph))        # Number of nodes in the subgraph
    densities[i] <- ifelse(num_nodes > 0, total_weight / (num_nodes^2), 0)
  }
  return(round(densities))  # Round to integers
}

# Calculate assortativity and densities
for (i in 1:11) {
  # Access the subgraph from the original graph (g)
  subgraph <- subnetworks[[paste0("subnetwork", i)]]
  
  # Ensure attributes are numeric
  V(subgraph)$population <- as.numeric(V(subgraph)$population)
  V(subgraph)$business <- as.numeric(V(subgraph)$business)
  
  # Calculate assortativity for the three metrics
  strength_assort <- assortcoef(
    adj = `rownames<-`(`colnames<-`(as_adjacency_matrix(subgraph, sparse = FALSE, attr = "weight"), NULL), NULL),
    directed = TRUE
  )$outin
  
  popu_assort <- assortcoef(
    adj = `rownames<-`(`colnames<-`(as_adjacency_matrix(subgraph, sparse = FALSE, attr = "weight"), NULL), NULL),
    f1 = V(subgraph)$population,
    f2 = NULL
  )$"f1-f1"
  
  business_assort <- assortcoef(
    adj = `rownames<-`(`colnames<-`(as_adjacency_matrix(subgraph, sparse = FALSE, attr = "weight"), NULL), NULL),
    f1 = V(subgraph)$business,
    f2 = NULL
  )$"f1-f1"
  
  # Store the assortativity results
  community_level_result$strength_assort[i] <- round(strength_assort, 3)
  community_level_result$popu_assort[i] <- round(popu_assort, 3)
  community_level_result$business_assort[i] <- round(business_assort, 3)
}

# Calculate densities for each graph and round to integers
community_level_result$density_2020 <- calculate_weighted_density(g_2020, community_membership)
community_level_result$density_2021 <- calculate_weighted_density(g_2021, community_membership)
community_level_result$density_2022 <- calculate_weighted_density(g_2022, community_membership)

# Calculate the total density for all three years
community_level_result$total <- community_level_result$density_2020 +
  community_level_result$density_2021 +
  community_level_result$density_2022

# Save results 
write_xlsx(community_level_result, path = "../result/community_level_result_assort_density.xlsx")

# Check the results
print(community_level_result)
```
