---
title: "dist_comm_cen"
author: "Zeyu Hu"
date: "2025-03-06"
output: html_document
---

```{r setup, include=FALSE}
library(igraph)
library(dplyr)
library(writexl)
library(tidyr)
library(sf)
library(ggplot2)
library(geojsonio)
library(readr)
library(writexl)
```

## Read data
```{r}
# Read the node and network data
nodes <- read.csv("../data/Seoul_node_info.csv")
network <- read.csv("../data/network.csv")

# Create a graph from the merged network data and name it g
g <- graph_from_data_frame(d = network, directed = TRUE)

# Set edge weights
E(g)$weight <- network$strength

# Add gu and dong attributes to each node
V(g)$gu <- nodes$gu[match(V(g)$name, nodes$node)]
V(g)$dong <- nodes$dong[match(V(g)$name, nodes$node)]
V(g)$population <- nodes$population[match(V(g)$name, nodes$node)]
V(g)$business <- nodes$business[match(V(g)$name, nodes$node)]

# Create the adjacency matrix
adjmatrix <- as_adjacency_matrix(g, sparse = FALSE, attr = "weight")
adjnull <- `rownames<-`(`colnames<-`(adjmatrix, NULL), NULL)
```
## density Table 1.
```{r echo=FALSE}
# Set data directory
data_dir <- "../data/"
years <- 2020:2022
file_list <- paste0(data_dir, "network_", years, ".csv")

# Read node information
nodes <- read.csv("../data/Seoul_node_info.csv")
node_to_gu <- setNames(nodes$gu, nodes$node)

# Count number of nodes per gu
gu_node_counts <- table(nodes$gu)
total_nodes <- sum(gu_node_counts)

# Initialize result lists
within_density_list <- list()
across_density_list <- list()
overall_density_list <- list()  # ← new

# Loop over each year
for (i in seq_along(file_list)) {
  file_path <- file_list[i]
  file_year <- as.character(years[i])
  
  if (!file.exists(file_path)) {
    message("File not found: ", file_path)
    next
  }
  
  # Read network data
  network_data <- read.csv(file_path)
  network_data$source_gu <- node_to_gu[as.character(network_data$source)]
  network_data$target_gu <- node_to_gu[as.character(network_data$target)]
  
  ### ----- 1. Per-gu within density -----
  within_density <- network_data %>%
    filter(source_gu == target_gu) %>%
    group_by(source_gu) %>%
    summarise(weight_sum = sum(strength, na.rm = TRUE)) %>%
    rename(gu = source_gu) %>%
    mutate(n = as.numeric(gu_node_counts[gu]),
           denom = n * n,
           value = weight_sum / denom,
           year = file_year) %>%
    select(gu, value, year)
  
  ### ----- 2. Per-gu across density -----
  across_density <- network_data %>%
    filter(source_gu != target_gu) %>%
    pivot_longer(cols = c(source_gu, target_gu), values_to = "gu") %>%
    group_by(gu) %>%
    summarise(weight_sum = sum(strength, na.rm = TRUE)) %>%
    mutate(n = as.numeric(gu_node_counts[gu]),
           denom = 2 * n * (total_nodes - n),
           value = weight_sum / denom,
           year = file_year) %>%
    select(gu, value, year)
  
  ### ----- 3. Overall network-level within & across density -----
  # 分子
  within_total <- network_data %>%
    filter(source_gu == target_gu) %>%
    summarise(weight_sum = sum(strength, na.rm = TRUE)) %>%
    pull(weight_sum)
  
  across_total <- network_data %>%
    filter(source_gu != target_gu) %>%
    summarise(weight_sum = sum(strength, na.rm = TRUE)) %>%
    pull(weight_sum)
  
  # 分母
  denom_within <- sum(as.numeric(gu_node_counts)^2)
  denom_across <- sum(as.numeric(gu_node_counts) * (total_nodes - as.numeric(gu_node_counts)))
  
  # density
  overall_density <- data.frame(
    year = file_year,
    type = c("within", "across"),
    value = c(within_total / denom_within, across_total / denom_across)
  )
  
  # Store results
  within_density_list[[file_year]] <- within_density
  across_density_list[[file_year]] <- across_density
  overall_density_list[[file_year]] <- overall_density
}

# Combine and reshape per-gu densities
within_density_df <- bind_rows(within_density_list) %>%
  pivot_wider(names_from = year, values_from = value, values_fill = 0) %>%
  arrange(gu)

across_density_df <- bind_rows(across_density_list) %>%
  pivot_wider(names_from = year, values_from = value, values_fill = 0) %>%
  arrange(gu)

# Combine overall network-level densities
overall_density_df <- bind_rows(overall_density_list) %>%
  pivot_wider(names_from = year, values_from = value)


# ----- 1. Prepare basic information -----

# Define the order of gu names based on existing gu_node_counts
gu_order <- names(gu_node_counts)

# Summarize population for each gu (district) by aggregating from nodes table
pop_by_gu <- nodes %>%
  group_by(gu) %>%
  summarise(population = sum(population, na.rm = TRUE)) %>%
  filter(gu %in% gu_order) %>%
  mutate(gu = factor(gu, levels = gu_order)) %>%
  arrange(gu)

# Number of dongs (sub-districts) per gu
dong_count <- data.frame(
  gu = gu_order,
  number_of_dongs = as.numeric(gu_node_counts)
)

# Merge population and dong counts
base_info <- left_join(pop_by_gu, dong_count, by = "gu")

# ----- 2. Merge per-gu within and across density -----

# Reshape wide → long format: columns are gu, year, density values
within_density_df_long <- within_density_df %>%
  pivot_longer(-gu, names_to = "year", values_to = "within")

across_density_df_long <- across_density_df %>%
  pivot_longer(-gu, names_to = "year", values_to = "across")

# Merge within and across together for each gu-year
density_all <- left_join(within_density_df_long, across_density_df_long, by = c("gu", "year"))

# Reshape long → wide format: separate columns for each year's within/across
density_wide <- density_all %>%
  pivot_wider(names_from = year, values_from = c(within, across), names_sep = "_")

# Merge with population and dong count
gu_summary <- left_join(base_info, density_wide, by = "gu")

# ----- 3. Create the "Total" row (for entire network) -----

total_row <- data.frame(
  gu = "Total",
  population = sum(gu_summary$population, na.rm = TRUE),
  number_of_dongs = sum(gu_summary$number_of_dongs),
  within_2020 = overall_density_df %>% filter(type == "within") %>% pull(`2020`),
  within_2021 = overall_density_df %>% filter(type == "within") %>% pull(`2021`),
  within_2022 = overall_density_df %>% filter(type == "within") %>% pull(`2022`),
  across_2020 = overall_density_df %>% filter(type == "across") %>% pull(`2020`),
  across_2021 = overall_density_df %>% filter(type == "across") %>% pull(`2021`),
  across_2022 = overall_density_df %>% filter(type == "across") %>% pull(`2022`)
)

# ----- 4. Combine all and finalize output -----

# Bind per-gu summary with the Total row
final_table <- bind_rows(gu_summary, total_row)
# reorder based on population
final_table <- final_table %>%
  filter(gu != "Total") %>%
  arrange(desc(population)) %>%
  bind_rows(filter(final_table, gu == "Total"))
### get final table for paper
# Step 1: divide population by 1000
final_table$population <- final_table$population / 1000

# Step 2: define columns to process
target_cols <- c("within_2020", "within_2021", "within_2022",
                 "across_2020", "across_2021", "across_2022")

# Step 3: extract total values for each column (last row of table)
total_row <- final_table[final_table$gu == "Total", target_cols]

# Step 4: loop and replace each target column
for (col in target_cols) {
  base_val <- as.numeric(total_row[[col]])
  final_table[[col]] <- sapply(final_table[[col]], function(x) {
    if (is.na(x)) return("")
    val_int <- round(x)
    ratio <- round(x / base_val, 2)
    paste0(val_int, " (", sprintf("%.2f", ratio), ")")
  })
}

writexl::write_xlsx(final_table, "../result/Table 1. Within_Across weighted mobility densities in Seoul (2020–2022).xlsx")
```



## community detection
```{r echo=FALSE}
# Infomap community detection
infomap_community <- cluster_infomap(g)

# Extract community membership results
community_membership <- membership(infomap_community)

# Convert to data frame and count the number of nodes in each community
membership_df <- data.frame(
  node = names(community_membership),
  community = community_membership
)

# Count the number of nodes per community and sort by descending size
community_sizes <- membership_df %>%
  group_by(community) %>%
  summarise(size = n()) %>%
  arrange(desc(size)) %>%
  mutate(new_community = row_number())  # Reassign community labels

# Map the new community labels back to the original data
membership_df <- membership_df %>%
  left_join(community_sizes, by = "community") %>%
  mutate(community = new_community) %>%
  dplyr::select(-new_community)

# Update the reordered community membership to the original format
community_membership <- setNames(membership_df$community, membership_df$node)
```

## centrality
```{r echo=FALSE}
# Calculate node strength (average of all and total strength)
strength_data <- data.frame(
  node = V(g)$name, 
  all_strength = strength(g, mode = "all", loops = FALSE),
  total_strength = strength(g, mode = "total")
) %>%
  mutate(strength = (all_strength + total_strength) / 2) %>%  # Average strength
  dplyr::select(node, strength)

# Load wdnet package for centrality computation
library(wdnet)

# Compute harmonic closeness centrality (outgoing)
myclose_out <- centrality(
  adj = adjmatrix,
  measure = "closeness", 
  closeness.control = list(method = "harmonic", distance = FALSE, mode = "out")
)
myclose_out <- as.data.frame(myclose_out)

# Compute harmonic closeness centrality (incoming)
myclose_in <- centrality(
  adj = adjmatrix,
  measure = "closeness", 
  closeness.control = list(method = "harmonic", distance = FALSE, mode = "in")
)
myclose_in <- as.data.frame(myclose_in)

# Compute Weighted PageRank (WPR) centrality
mywpr_null <- centrality(
  adj = adjmatrix,
  measure = "wpr", 
  wpr.control = list(gamma = 0.85, theta = 1)
)
mywpr_null <- as.data.frame(mywpr_null)

# Combine all centrality measures into one data frame
centrality <- data.frame(
  name = myclose_out$name,
  closeness_out = myclose_out$closeness,
  closeness_in = myclose_in$closeness,
  wpr = mywpr_null$wpr
)

# Merge with node strength
centrality <- centrality %>% 
  left_join(strength_data, by = c("name" = "node"))
```

## map Figure 2 (a)
```{r}
# Read TopoJSON file
seoul_map <- geojson_read("../data/skorea-submunicipalities-2018-topo.json", what = "sp")

# Assume seoul_map is already in sf format, filter Seoul region
seoul_map_11 <- st_as_sf(seoul_map[substr(seoul_map@data$code, 1, 2) == "11", ])

# Extract gu information (first 4 digits of the code)
seoul_map_11 <- seoul_map_11 %>%
  mutate(gu = substr(code, 1, 4))  # Add gu column

# Merge by gu and calculate the boundary of each gu
gu_boundaries <- seoul_map_11 %>%
  group_by(gu) %>%
  summarise(geometry = st_union(geometry))  # Merge geometry

# Extract community detection results and join to the map data
membership_df <- data.frame(
  code = names(community_membership),
  community = as.factor(community_membership)
)

seoul_map_11 <- seoul_map_11 %>%
  left_join(membership_df, by = c("code" = "code"))

gu_boundaries_lines <- st_cast(gu_boundaries, "MULTILINESTRING")

map_color <- nodes %>% 
  mutate(node = as.character(node))

# Add population data to map
seoul_map_11 <- seoul_map_11 %>% 
  left_join(map_color, by = c("code" = "node"))  # Match map code with nodes$node

# Merge centrality data with map data
seoul_map_11 <- seoul_map_11 %>%
  left_join(centrality, by = c("code" = "name"))

# Manually assign a color to each community
community_colors <- c(
  "1" = "#d35f00",  # Color for community 1
  "2" = "#fd7c1a",  # Color for community 2
  "3" = "#fcff07",  # Color for community 3
  "4" = "#fe9376",  # Color for community 4
  "5" = "#f3dee0",  # Color for community 5
  "6" = "#ffbd15",  # Color for community 6
  "7" = "#a0c9e5",  # Color for community 7
  "8" = "#1d9bf7",  # Color for community 8
  "9" = "#303cf9",  # Color for community 9
  "10" = "#b4403e", # Color for community 10
  "11" = "#603c87"  # Color for community 11
)

# Plot community map
community_map <- ggplot() +
  geom_sf(data = seoul_map_11, aes(fill = community), color = "grey", size = 0.2) +  # Grey lines for dong boundaries
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # Thick black lines for gu boundaries
  scale_fill_manual(values = community_colors) +  # Use manually defined colors
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) +
  guides(
    fill = guide_legend(nrow = 2, byrow = TRUE)
  )
#ggsave("../result/Figure 2(a). Community_map.png", community_map, width = 8, height = 6, dpi = 300, bg = "white")
```

## strength distribution(powerlaw test)
```{r echo=FALSE}
# Load required package
library(poweRlaw)

# Perform power-law test for in_strength
strength <- strength_data$strength
strength <- strength / 1000000
strength <- floor(strength)

# Create power-law distribution object
m_pl_in <- displ$new(strength)

# Estimate parameters
est_in <- estimate_xmin(m_pl_in)
m_pl_in$setXmin(est_in)

# Set random seed
set.seed(123)

# Perform bootstrap test
bs_in <- bootstrap_p(m_pl_in, no_of_sims = 100, threads = 1)

# Output in-strength results
cat("strength P-value:", bs_in$p, "\n")
cat("strength xmin:", m_pl_in$xmin, "\n")
cat("strength pars (alpha):", m_pl_in$pars, "\n")
cat("strength xmin standard error:", sd(bs_in$bootstraps$xmin), "\n")
cat("strength pars standard error:", sd(bs_in$bootstraps$pars), "\n\n")
cat("Number of dongs exceed the xmin:", sum(strength > 73), 
    ", accounting for", sprintf("%.2f%%", sum(strength[strength > 73]) / sum(strength) * 100), 
    "of the total strength.\n")
```
strength P-value: 0.45
strength xmin: 73
strength pars (alpha): 3.706917
strength xmin standard error: 8.813442
strength pars standard error: 0.3002339
Number of dongs exceed the xmin: 138 , accounting for 55.53% of the total in-strength


## strength dist(plot)_Figure 1 (a) (b)
```{r echo=FALSE}
library(ggplot2)
library(ggpubr)

# Calculate the CDF of Strength
cdf_data <- data.frame(
  strength = sort(strength),
  cdf = ecdf(strength)(sort(strength))
)

# Calculate right-tail cumulative distribution (1 - CDF)
cdf_data$tail_cdf <- 1 - cdf_data$cdf

# Plot the right-tail cumulative distribution of Strength
strength_plot <- ggplot(cdf_data, aes(x = strength, y = tail_cdf)) +
  geom_point(aes(color = ifelse(strength >= 73, "Above Threshold", "Below Threshold"))) +
  scale_y_log10() +
  scale_x_log10(breaks = c(1, 10, 73, 100), expand = c(0, 0)) +
  labs(
    x = "Node In-Strength (log scale)",
    y = "Survival (log scale)"
  ) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 16),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  ) +
  scale_color_manual(values = c("Below Threshold" = "lightblue", "Above Threshold" = "lightcoral")) +
  {
    xmin <- 73
    alpha <- 3.706917
    fitted_x <- seq(xmin, max(cdf_data$strength), length.out = 100)
    fitted_y <- (fitted_x / xmin)^(-alpha + 1)
    y_baseline <- cdf_data$tail_cdf[cdf_data$strength == xmin]
    fitted_y <- fitted_y * y_baseline
    geom_line(data = data.frame(strength = fitted_x, tail_cdf = fitted_y),
              aes(x = strength, y = tail_cdf), color = "blue", linetype = "dashed", linewidth = 0.8)
  } +
  geom_vline(xintercept = 73, linetype = "dashed", color = "black")

# Save the plot as PNG file
#ggsave(filename = "../result/Figure 1(a). Strength_dist.png",  plot = strength_plot, width = 6, height = 6, dpi = 300, bg = "white")

strength_map <- ggplot() +
  geom_sf(data = seoul_map_11, aes(fill = factor(strength > 73000000, levels = c(TRUE, FALSE))), 
          color = "grey", size = 0.2) +  # dong boundaries in grey
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu boundaries in thick black
  scale_fill_manual(values = c("TRUE" = "lightcoral", "FALSE" = "lightblue"),  
                    labels = c("Above Threshold", "Below Threshold")) +  # Ensure red on the left
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE, title = NULL))

#ggsave(filename = "../result/Figure 1(b). Strength_map.png",  plot = strength_map, width = 8, height = 6, dpi = 300, bg = "white")
```

## Within/Across weighted Density Figure 2(b)
```{r echo=FALSE}
library(igraph)
library(dplyr)

# Get edge list including weights
edges_df <- igraph::as_data_frame(g, what = "edges")

# Map community membership to edge list
edges_df <- edges_df %>%
  mutate(
    source_community = as.factor(community_membership[as.character(from)]),
    target_community = as.factor(community_membership[as.character(to)])
  )

# Count number of nodes in each community
community_sizes <- membership_df %>%
  group_by(community) %>%
  summarise(size = n(), .groups = "drop")

# Compute weighted density matrix
density_matrix <- edges_df %>%
  group_by(source_community, target_community) %>%
  summarise(
    total_weight = sum(weight), # Total weight between community pairs
    .groups = "drop"
  ) %>%
  left_join(community_sizes, by = c("source_community" = "community")) %>%
  rename(size_source = size) %>%
  left_join(community_sizes, by = c("target_community" = "community")) %>%
  rename(size_target = size) %>%
  mutate(
    possible_edges = ifelse(
      source_community == target_community, # Check for within-community
      size_source^2,                        # Within-community: n_i^2
      2 * size_source * size_target         # Between-community: 2 * n_i * n_j
    ),
    weighted_density = total_weight / possible_edges # Weighted density
  ) %>%
  dplyr::select(source_community, target_community, weighted_density)

# Convert to matrix format
density_matrix_wide <- density_matrix %>%
  tidyr::pivot_wider(
    names_from = target_community,
    values_from = weighted_density,
    names_prefix = "Community_"
  ) %>%
  arrange(source_community)

# Convert the matrix to final format
density_matrix_final <- as.matrix(density_matrix_wide %>% dplyr::select(-source_community))
rownames(density_matrix_final) <- paste0("Community_", density_matrix_wide$source_community)

# Print the result
print("Weighted Density Matrix:")
print(density_matrix_final)

# Divide each element by 1000 and round to 2 decimal places
density_matrix_final_divided <- round(density_matrix_final / 1000, 2)

# Convert matrix to data frame (CSV-friendly format)
density_matrix_final_df <- as.data.frame(density_matrix_final_divided)

# Load required packages
library(ggplot2)
library(reshape2)

# Convert the matrix to long format
density_long <- reshape2::melt(as.matrix(density_matrix_final_divided))

# Ensure column names are correct
colnames(density_long) <- c("source", "target", "Density")

# Replace labels with cleaner format
density_long$source <- gsub("Community_", "C-", density_long$source)
density_long$target <- gsub("Community_", "C-", density_long$target)

# Ensure x and y axis order matches input data
unique_labels <- unique(density_long$source) # Get original order
density_long$source <- factor(density_long$source, levels = rev(unique_labels)) # Reverse y-axis order
density_long$target <- factor(density_long$target, levels = unique_labels) # Keep x-axis order

# Log-smooth the data (adjusted density)
density_long$Adjusted_Density <- log(density_long$Density)

# Plot heatmap
W_A_density_heatmap <- ggplot(density_long, aes(x = target, y = source, fill = Adjusted_Density)) + 
  geom_tile(color = "white") + # Add white border
  geom_text(aes(label = sprintf("%.2f", Adjusted_Density)), size = 3, color = "black") + # Add values in cells
  scale_fill_gradientn(
    colors = c("white", "red"),
    name = "Log of Weighted Density (in thousands)" # Update legend title
  ) + 
  scale_x_discrete(position = "top") + # Move x-axis to top
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    legend.position = "bottom", # Place legend at bottom
    legend.direction = "horizontal" # Horizontal legend layout
  ) + 
  labs(x = "Target", y = "Source")
#ggsave("../result/Figure 2(b). W_A_density_heatmap.png", W_A_density_heatmap, width = 8, height = 6, dpi = 600, bg = "white")
```

## WPR top/bottom 10
```{r}
seoul_map_11 <- seoul_map_11 %>% mutate(Mobility = (strength / sum(strength)) * 2)

top_10 <- seoul_map_11 %>% 
  arrange(desc(wpr)) %>% 
  slice_head(n = 10) %>% 
  mutate(rank = row_number()) %>% 
  dplyr::select(rank, dong, strength, gu = gu.y, community, Mobility)


bottom_10 <- seoul_map_11 %>% 
  arrange(wpr) %>% 
  slice_head(n = 10) %>% 
  mutate(rank = row_number()) %>% 
  dplyr::select(rank, dong, strength, gu = gu.y, community, Mobility)

#write_xlsx(top_10, "../result/Table 2(a). Top10wpr.xlsx")
#write_xlsx(bottom_10, "../result/Table 2(b). Bottom10wpr.xlsx")
```

## Appendix. Table S1. community 
```{r echo=FALSE}
# Ensure consistent column types
membership_df <- membership_df %>%
  mutate(code = as.integer(code))  # Convert code to integer

nodes <- nodes %>%
  mutate(node = as.integer(node))  # Ensure node is also integer

# Merge membership and node info, compute community-level statistics
community_stats <- membership_df %>%
  left_join(nodes, by = c("code" = "node")) %>%
  group_by(community) %>%
  summarise(
    size = n(),
    total_population = sum(population, na.rm = TRUE),
    total_business = sum(business, na.rm = TRUE),
    total_poverty = sum(poverty, na.rm = TRUE),
    avg_population = total_population / size,
    avg_business = total_business / size,
    avg_poverty = total_poverty / total_population
  ) %>%
  mutate(
    size = as.numeric(size),  # Convert to numeric
    total_population = round(total_population, 2),
    total_business = round(total_business, 2),
    total_poverty = round(total_poverty, 2),
    avg_population = round(avg_population, 2),
    avg_business = round(avg_business, 2),
    avg_poverty = round(avg_poverty, 4)
  ) %>%
  arrange(desc(size))

# Compute total within and across community weights
community_weight <- edges_df %>%
  group_by(source_community, target_community) %>%
  summarise(
    total_weight = sum(weight),  # Total weight between community pairs
    .groups = "drop"
  )

# Merge weight contributions into community_stats
community_stats <- community_stats %>%
  left_join(
    community_weight %>%
      mutate(
        source_contribution = if_else(source_community == target_community, total_weight, total_weight / 2),
        target_contribution = if_else(source_community != target_community, total_weight / 2, 0)
      ) %>%
      group_by(source_community) %>%
      summarise(weight_sum = sum(source_contribution)) %>%
      rename(community = source_community) %>%
      bind_rows(
        community_weight %>%
          filter(source_community != target_community) %>%
          group_by(target_community) %>%
          summarise(weight_sum = sum(total_weight / 2)) %>%
          rename(community = target_community)
      ) %>%
      group_by(community) %>%
      summarise(
        weight_sum = sum(weight_sum),
        proportion = weight_sum / sum(community_weight$total_weight)
      ),
    by = "community"
  )

# View result
print(community_stats)
#write_xlsx(community_stats, "../result/Table S1. Community stats.xlsx")
```

## Spearman correlation
```{r echo=FALSE}
size_rank <- rank(community_stats$size)
population_rank <- rank(community_stats$total_population)
business_rank <- rank(community_stats$total_business)
poverty_rank <- rank(community_stats$total_poverty)

# compute spearman correlation
correlation_population <- cor(size_rank, population_rank, method = "spearman")
correlation_business <- cor(size_rank, business_rank, method = "spearman")
correlation_poverty <- cor(size_rank, poverty_rank, method = "spearman")

# cat result
cat("Spearman correlation coefficients:\n")
cat("Size vs Total Population:", correlation_population, "\n")
cat("Size vs Total Business:", correlation_business, "\n")
cat("Size vs Total Poverty:", correlation_poverty, "\n")
```

Spearman correlation coefficients:
Size vs Total Population: 0.9863117 
Size vs Total Business: 0.9497816 
Size vs Total Poverty: 0.8082276 

## Appendix. Figrue S1
```{r echo=FALSE}
# Set data directory
data_dir <- "../data/monthly/"

# Generate file names for all months from 2020 to 2022
years <- 2020:2022
months <- sprintf("%02d", 1:12)  # 01, 02, ..., 12
file_dates <- as.vector(outer(years, months, paste0))  # 202001, 202002, ..., 202212
file_list <- paste0(data_dir, "network_", file_dates, ".csv")  # Full file paths

# Read node information
nodes <- read.csv("../data/Seoul_node_info.csv")
node_to_gu <- setNames(nodes$gu, nodes$node)

# Initialize result lists
within_density_list <- list()
across_density_list <- list()

# Process each file
for (i in seq_along(file_list)) {
  file_path <- file_list[i]
  file_date <- file_dates[i]  # Extract date, e.g., "202001"

  if (!file.exists(file_path)) {
    message("File not found: ", file_path)
    next  # Skip missing files
  }
  
  # Read network data
  network_data <- read.csv(file_path)
  
  # Add gu information
  network_data$source_gu <- node_to_gu[as.character(network_data$source)]
  network_data$target_gu <- node_to_gu[as.character(network_data$target)]
  
  # Calculate within_density
  within_density <- network_data %>%
    filter(source_gu == target_gu) %>%
    group_by(source_gu) %>%
    summarise(value = sum(strength, na.rm = TRUE)) %>%
    rename(gu = source_gu) %>%
    mutate(date = file_date)
  
  # Calculate across_density
  across_density <- network_data %>%
    filter(source_gu != target_gu) %>%
    pivot_longer(cols = c(source_gu, target_gu), values_to = "gu") %>%
    group_by(gu) %>%
    summarise(value = sum(strength, na.rm = TRUE)) %>%
    mutate(date = file_date)
  
  # Store in lists
  within_density_list[[file_date]] <- within_density
  across_density_list[[file_date]] <- across_density
}

# Combine all time points
within_density_df <- bind_rows(within_density_list) %>%
  pivot_wider(names_from = date, values_from = value, values_fill = 0) %>%
  arrange(gu)

across_density_df <- bind_rows(across_density_list) %>%
  pivot_wider(names_from = date, values_from = value, values_fill = 0) %>%
  arrange(gu)

# Extract and sort column names
correct_order <- c("gu", sort(setdiff(colnames(within_density_df), "gu")))

# Reorder columns
within_density_df <- within_density_df[, correct_order]
across_density_df <- across_density_df[, correct_order]

# Reshape to long format
within_density_long <- within_density_df %>%
  pivot_longer(cols = -gu, names_to = "date", values_to = "within_density")

across_density_long <- across_density_df %>%
  pivot_longer(cols = -gu, names_to = "date", values_to = "across_density")

# Convert date format to Year-Month (YYYY-MM)
within_density_long$date <- format(as.Date(paste0(within_density_long$date, "01"), format="%Y%m%d"), "%Y-%m")
across_density_long$date <- format(as.Date(paste0(across_density_long$date, "01"), format="%Y%m%d"), "%Y-%m")

# Ensure date is a factor and ordered chronologically
within_density_long$date <- factor(within_density_long$date, levels = unique(within_density_long$date))
across_density_long$date <- factor(across_density_long$date, levels = unique(across_density_long$date))

# Add labels
within_density_long$variable <- "Within"
across_density_long$variable <- "Across"

# Convert to millions
within_density_long <- within_density_long %>% mutate(density = within_density / 1e6)
across_density_long <- across_density_long %>% mutate(density = across_density / 1e6)

# Combine datasets
density_data <- bind_rows(within_density_long, across_density_long)

density_data$variable <- factor(density_data$variable, levels = c("Within", "Across"))

# Plot
WA_25gu <- ggplot(density_data, aes(x = date, y = density, color = gu, group = gu)) +
  geom_line() +
  facet_grid(. ~ variable, scales = "fixed") +  # Facet horizontally by 'variable'
  labs(x = "Year-Month", y = "Density (in million)") +
  theme_minimal(base_size = 14) +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    strip.background = element_rect(fill = "grey80"),
    strip.text = element_text(size = 14, face = "bold"),
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),  # Rotate date labels
    axis.text = element_text(color = "black"),
    axis.title.y = element_text(size = 16)
  )

ggsave("../result/Figure S1. WA_25gu.png", WA_25gu, width = 15, height = 8, dpi = 300, bg = "white")
```

## Appendix. Figure S2
```{r echo=FALSE}
population_map <- ggplot() + 
  geom_sf(data = seoul_map_11, aes(fill = population / 1000), color = "grey", size = 0.2) +  # dong boundaries in grey
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu boundaries in thick black
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Population") +  # color by population
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) + 
  guides(
    fill = guide_colorbar(barwidth = 10, barheight = 0.5)  # adjust legend size
  )
#ggsave("../result/Figure S2(a). Population.png", population_map, width = 8, height = 6, dpi = 300, bg = "white")

incidence_map <- ggplot() + 
  geom_sf(data = seoul_map_11, aes(fill = (incidence / gu_popu) * 100), color = "grey", size = 0.2) +  # dong boundaries in grey
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu boundaries in thick black
  scale_fill_gradient(low = "coral", high = "darkred", 
                      name = "Incidence (%)", 
                      labels = percent_format(scale = 1)) +  # show percentage format
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) + 
  guides(
    fill = guide_colorbar(barwidth = 10, barheight = 0.5)  # adjust legend size
  )
#ggsave("../result/Figure S2(b). Incidence.png", incidence_map, width = 8, height = 6, dpi = 300, bg = "white")

business_map <- ggplot() + 
  geom_sf(data = seoul_map_11, aes(fill = business / 1000), color = "grey", size = 0.2) +  # dong boundaries in grey
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu boundaries in thick black
  scale_fill_gradient(low = "lightgreen", high = "darkgreen", name = "Business") +  # color by number of businesses
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) + 
  guides(
    fill = guide_colorbar(barwidth = 10, barheight = 0.5)  # adjust legend size
  )
#ggsave("../result/Figure S2(c). Business.png", business_map, width = 8, height = 6, dpi = 300, bg = "white")

poverty_map <- ggplot() + 
  geom_sf(data = seoul_map_11, aes(fill = poverty / 1000), color = "grey", size = 0.2) +  # dong boundaries in grey
  geom_sf(data = gu_boundaries_lines, color = "black", size = 1.5) +  # gu boundaries in thick black
  scale_fill_gradient(low = "coral", high = "darkred", name = "Poverty") +  # color by number of welfare beneficiaries
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    plot.background = element_rect(fill = "white", color = NA)
  ) + 
  guides(
    fill = guide_colorbar(barwidth = 10, barheight = 0.5)  # adjust legend size
  )
#ggsave("../result/Figure S2(d). Poverty.png", poverty_map, width = 8, height = 6, dpi = 300, bg = "white")
```